### 2016-04-26 definitions.tex
With Comments
With Dongxiang's comments

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ denote the set of objects in concern, $\mathbb{T} = \{1,2,...,m\}$ be the descritized sequence of timestamps. We use $t_i$ to denote the $i^{th}$ entry in a time sequence.

Given a time sequence $T \subseteq \mathbb{T}$, let $|T|$ be the cardinality of the sequence and $T.s,T.e$ be the start and end of the sequence. We say a sequence $T$ is \emph{(fully)consecutive}
if and only if $\forall T.s \leq t_i < T.e$, $t_{i+1} = t_i + 1$. A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt. $T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive. For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt. $T$. We then define the $l$-consecutiveness as follows:

\begin{definition}[$l$-consecutive]
A time sequence $T$ is $l$-consecutive iff $\forall$ its maximal consecutive subsequences $T^m$, $|T^m| \geq l$.
\end{definition}

Take $T=\{1,2,3,5,6\}$ as an example. $T$ is not $3$-consecutive since $\{5,6\}$ is a maximally consecutive subsequence with cardinality less than $3$. $T$ is $2$-consecutive since both its two maximally consecutive subsequences are of the sizes greater or equal to $2$. It is notable that, for a sequence $T$, all its maximally consecutive subsequences are non-overlapping. Therefore, we are able to order the maximally consecutive subsequences. Let $T^m_{i}$ denote the $i^{th}$ maximally consecutive sequences wrt. $T$, then we can define the $g$-separated of $T$ as follows:

\begin{definition}[$g$-separated]
A time sequence $T$ is $g$-separated iff $\forall T^m_{i+1}.s - T^m_{i}.e \leq g$
\end{definition}

@@

Although the generalized co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting objects with arbitrary spatio-shaped clusters.

@@

>>>>

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ denote the set of objects in concern, $\mathbb{T} = \{1,2,...,m\}$ be the descritized sequence of timestamps. We use $T[i]$ to denote the $i^{th}$ entry in a time sequence.

Given a time sequence $T \subseteq \mathbb{T}$, let $|T|$ be the cardinality of the sequence. We say a sequence $T$ is \emph{(fully)consecutive}
if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$. A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt. $T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive. For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt. $T$. We then define the $L$-consecutiveness as follows:

\begin{definition}[$L$-consecutive]
A time sequence $T$ is $L$-consecutive iff $\forall$ its maximal consecutive subsequences $T^m$, $|T^m| \geq L$.
\end{definition}

Take $T=\{1,2,3,5,6\}$ as an example. $T$ is not $3$-consecutive since $\{5,6\}$ is a maximally consecutive subsequence with cardinality less than $3$. $T$ is $2$-consecutive since both its two maximally consecutive subsequences are of the sizes greater or equal to $2$. It is notable that, for a sequence $T$, all its maximally consecutive subsequences are non-overlapping.

We then define the $G$-separateness as follows:

\begin{definition}[$G$-separated]
A time sequence $T$ is $G$-separated iff $\forall T[i],T[i+1] \in T, T[i+1]-T[i] \leq G$
\end{definition}

@@

Although the generalized co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting objects with arbitrary spatio-shaped clusters. Therefore in this paper, we mainly consider density-based clustering.

@@

Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}
\begin{tabular}{|c|c|}
\hline 
$Tr_i$ & Trajectory of object $i$\\ 
\hline
$S_t$ & Snapshot of objects at time $t$ \\
\hline 
$\mathbb{O}$ & Set of objects \\ 
\hline 
$\mathbb{T}$ & Global time sequence \\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$Sr_i $ &  The star structure of object $i$ \\
\hline 
\end{tabular} 
\caption{Notions that will be used}
\end{table}

### 2016-04-26 optimization.tex
With Comments
With Dongxiang's comments

\section{Optimization}
We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
lies in two factors. The size of each $Sr_s$ and the level the apriori runs.
In this section, we describe to optimization to reduce the two factors
respectively.

\subsection{Edge Simplification}
Each edge $e(s,t)$ in $Sr_s$ contains a time sequence $T$ 
which represent the co-occurrence of $s$ and $t$. We notice that the edge
between $s$ and $t$ is not always necessary. For example, if an edge has a
cardinality less than $K$, then it is not necessary to include this edge to $Sr_s$.
This motivates to simplify the edges in $Sr_s$ to boost the overall performance.

We first define the \emph{Pseudo-consecutiveness} of a time sequence as follows:
\begin{definition}[Pseudo-consecutiveness]
Given a parameter $G$, a sequence $T$ is \emph{pseudo-consecutive} if and only
if for any $i\in (0, |T|)$, $T[i] - T[i-1] \leq G$
\end{definition}
For example, let $G = 2$, then the sequence $T_1=\{1, 2, 4, 5\}$ is pseudo-consecutive
while $T_2=\{1,4,5,6,8\}$ is not pseudo-consecutive.

@@

\begin{definition}[Partly Candidate Sequence]
Given the pattern parameters: $L,K,G$, a sequence $T$ is 
a \emph{partly candidate} sequence if exist one of its maximal pseudo-consecutive
subsequence $T'$ such that $T'$ confirms to $L,K,G$.
\end{definition}

For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11)$ 
is a \emph{partly candidate sequence} since $T_1[0:3] = (1,2,4,5,6)$ is a valid
pattern wrt. $L,K,G$. In contrast, $T_2=(1,2,5,6,7)$ is not a valid partly candidate sequence.

Observing that only partly candidate sequence can be potentially included in a 
pattern. Therefore, given an edge $e(s,t)=T \in Sr_s$, if $T$ is not a partly
candidate sequence, then this edge can be pruned from $Sr_s$. To efficiently
test whether a given sequence is partly candidate, we define the \emph{Fully Candidate Sequence}:

@@

We use the following theorem to state the completeness and correctness of our 
edge reduction algorithm.
\begin{theorem}[Completeness of Algorithm~\ref{algo:simp_prune}]
For a sequence $T$, let $T_1$ be the result of $T$ after algorithm~\ref{algo:simp_prune},
if $\exists T' \subseteq T$ and $T'$ is included in a pattern $P$, then $T' \subseteq T_1$.
\end{theorem}

\begin{proof}
OMITTED FOR NOW
\end{proof}
By utilizing the edge simplification technique, the size of $Sr_s$ can be greatly reduced. If
an edge cannot be reduced to a full candidate sequence, then it is directly removed from $Sr_s$.
If an edge can be reduced to a full candidate sequence, replacing itself with its full candidate sequence 
would result in a more compact storage.

\subsection{Pruning Apriori Mining}
During the apriori phase, we are repeatedly join candidate pattern in different levels to generate a larger set
of a pattern. We notice that, such joins can be early terminated 
by utilizing the property of GCMP. The intuition is that when we are trying to store a level of candidate, if its
temporal sequence is not a \emph{partly candidate} sequence, then it should able to generate new candidates and thus it
can be removed from that level of candidate. This \emph{apriori property} 
is explicitly described as in the follow theorem:

\begin{theorem}[Apriori Property of GCMP]
Given the temporal parameters $L,G,K$ of GCMP, for a candidate $cand$ in Algorithm~\ref{algo:apriori_mining},
if $cand.T$ cannot be reduced to a full candidate sequence, then $cand$ can be pruned.
\end{theorem}
\begin{proof}
OMITTED FOR NOW
\end{proof}

Utilizing the \emph{Apriori Property}, the new candidate in each level is greatly reduced, which is shown in
the experiment session.

>>>>

\section{Optimization}
We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
lies in two factors. The size of each $Sr_s$ and the size of candidates in each level of Apriori.
In this section, we provide several optimizations to boost the bottlenecks.

\subsection{Edge Reduction by Direction}
The first spot for reducing the size of $Sr_s$ is to remove the replicated edges. As shown in Algorithm~\ref{algo:spm_overview}, each edge in the conceptual graph is replicated twice in generating the star-structure. The purpose of replication is to ensure the completeness of star partition. However, this replication can be avoided if we choose an appropriate way of partitioning.

We design the edge partitioning method by edge direction. Instead of building a conceptual graph that is undirected, we create the directed conceptual graph as follows: First, we assign each object a unique number. Then
for a cluster $C_t$ in snapshot $S_t$, for any pair $(u,v) \in C_t$, an edge $e(u,v) = \{t\}$ is created if $u < v$. It is easy to see that the directed conceptual graph is a DAG. We then create each $Sr_u$ by including all the outgoing edges of $u$. By so doing, each edge is assigned to only one star, thus avoids the replications. We use the following theorem to ensure the completeness of the edge direction method.

\begin{theorem}[Sound and Completeness of Edge Direction]
Star partition with edge direction is sound and complete.
\end{theorem}
\begin{proof}
It is notable that each star is a subset of original trajectories, thus the soundness is trivially true. For completeness, if $P$ is valid pattern, then let $s$ be the object of the smallest number in $P.O$, i.e., $s=\min_{o \in P.O}(o)$. Since $s$ is smallest and the all other objects in $P.O$ is connected with $s$. Therefore, $P.O \equiv Sr_s$, which indicates that $P.O$ is also a pattern in $Sr_s$.
\end{proof}
An example of edge direction is shown in Figure~\ref{fig:star_partition}. As shown,
by adapting the direction method, half the size of $S_r$'s is reduced. This clearly brings efficiency in both shuffling and apriori mining.

\subsection{Edge Simplification}
Each edge $e(s,t)$ in $Sr_s$ contains a time sequence $ET$ 
which represent the co-occurrence of $s$ and $t$. We notice that the edge between $s$ and $t$ is not always necessary. For example, if an edge has a
cardinality less than $K$, it is unnecessary to include this edge to $Sr_s$ since it cannot contribute to any patterns.
This motivates us to simplify the edges in $Sr_s$ to boost the overall performance.

We first define the \emph{Pseudo-consecutiveness} of a time sequence as follows:
\begin{definition}[Pseudo-consecutiveness]
Given a parameter $G$, a sequence $T$ is \emph{pseudo-consecutive} if and only
if for any $i\in [1, |T|]$, $T[i] - T[i-1] \leq G$
\end{definition}
For example, let $G = 2$, then the sequence $T_1=\{1, 2, 4, 5\}$ is pseudo-consecutive
while $T_2=\{1,4,5,6,8\}$ is not pseudo-consecutive.

@@

\begin{definition}[Partly Candidate Sequence]
Given the pattern parameters: $L,K,G$, a sequence $T$ is 
a \emph{partly candidate} sequence if exists one of its maximal pseudo-consecutive
subsequence $T'$ such that $T'$ confirms to $L,K,G$.
\end{definition}

For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11)$ 
is a \emph{partly candidate sequence} since $T_1[1:5] = (1,2,4,5,6)$ is a valid
pattern wrt. $L,K,G$. In contrast, $T_2=(1,2,5,6,7)$ is not a valid partly candidate sequence.

Observing that only partly candidate sequence can be potentially contribute to a 
pattern. Therefore, given an edge $e(s,t)=T \in Sr_s$, if $T$ is not a partly
candidate sequence, it can be pruned from $Sr_s$. To efficiently
test whether a given sequence is partly candidate, we define the \emph{Fully Candidate Sequence}:

@@

We use the following theorem to state the completeness and correctness of our 
edge reduction algorithm.
\begin{theorem}[Soundness and Completeness Edge Simplification]
Star partition with edge simplification is sound and complete.
\end{theorem}

\begin{proof}
Soundness of the star partition is not affected by edge simplification since each star is a subset of original trajectory. For completeness, consider a sequence $T$, let $T_1$ be the result of $T$ after first round of simplification. By the nature of the first round of simplification, if $P.T \subseteq T$, then $P.T \subseteq T_1$. In the second round of simplification, only the pseudoconsecutive parts with size less than $K$ are removed. This means, the removed parts is not able to contribute to any patterns. Thus if $P.T \subseteq T$, then $P.T \subseteq T'$. 
\end{proof}
By leveraging the edge simplification, the size of $Sr_s$ can be greatly reduced. If
an edge cannot be reduced to a full candidate sequence, then it is directly removed from $Sr_s$.
If an edge can be reduced to a full candidate sequence, replacing itself by the full candidate sequence results in a more compact storage.

\subsection{Pruning Apriori Mining}
During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
of a patterns. We notice that, such joins can be early terminated 
by utilizing the monotonic property of GCMP. The intuition is that when we are trying to store a candidate, if its
temporal sequence is not a \emph{partly candidate} sequence, then it cannot generate full candidate and thus it
can be pruned. This \emph{monotonic property} 
is explicitly described as in the follow theorem:

\begin{theorem}[Monotonic Property of GCMP]
Given the temporal parameters $L,G,K$, for a candidate $cand$ in Algorithm~\ref{algo:apriori_mining},
if $cand.T$ cannot be reduced to a partly candidate sequence, then $cand$ can be pruned.
\end{theorem}
\begin{proof}
Let $cand_i$ be a $i$-pattern. If $cand_i$ is generated from $cand_j$ where $j < i$, then if $cand_j.T \subseteq cand_i.T$. That is as the level goes up, the time sequence set of a candidate shrinks. Therefore, if $cand_j.T$ is not a partly candidate sequence, $cand_i.T$ cannot be a partly candidate sequence.
\end{proof}

With the help of the \emph{Monotonic Property}, the number of new candidates in each level is greatly reduced. We verify this in the experiment session as well.

### 2016-04-26 system.tex
With Comments
With Dongxiang's comments

\section{Preliminary on Apache Spark}
Apache Spark is the modern parallel processing platform
based on Resilient-Distributed-Dataset (RDD), which
is open-sourced by UC Berkeley. Spark differs from
traditional MapReduce framework (e.g., Hadoop) in the 
following features:
\begin{enumerate}
\item{It supports general computation DAGs beyond the two-stage MapReduce topologcy.}
\item{The execution engine can tolerate the loss of any works}
\item{It provides an in-memory storage abstraction called Resilient Distributed Datasets (RDDs). that 
lets applications keep data in memory, and automatically reconstructs the lost partitions upon failures.}
\end{enumerate}

In MapReduce-like systems, the major bottleneck is the \emph{shuffle} operation. 
In the \emph{shuffle} operation, data are re-partitioned and send to executors
via networks. Such operation is more costly than CPU and disk I/Os, which contribute
most in MapReduce-like applications.

TO BE ADDED....

\section{Mining Generalized Co-moving Pattern}
The outline of GCMP mining is to first cluster objects at
each snapshots and followed by mining the patterns among clusters
of different snapshots. In Spark scenario, 
the first step can be easily performed in parallel. 
This is because the objects at each snapshots are independent. Therefore, we
can partition the trajectories based on snapshots to achieve parallelism. 
In contrast, naively design the 
the second step may suffer from inter-executor communications.

\subsection{Temporal Replication and Mining}
The straightforward method of parallelizing GCMP mining is to partition
the trajectories in the temporal domain. A simple but effective method
is to group neighborhood snapshots in to a partition, such that all patterns
can be mined within a partition. In order to achieve the \emph{completeness},
some of the snapshots need to be replicated on multiple executors.
We thus call this method the \emph{Temporal Replication and Mining} approach. 
The algorithm is presented as in Algorithm~\ref{algo:trm_overview}.

@@

\subsubsection{Temporal Replication Partition}
In order to reduce the shuffling cost, the data to be replicated should be
kept to a minimum. To control the number of snapshots that are replicated, 
we use the following theorem to facilitate a partition:

\begin{theorem}[Completeness of Replication Partition]
\label{thm:replication_partition}
For each snapshot $S_t$, a partition $Par_t = \{S_t, S_{t+1},...,S_{t+(K-1)*G+K}\}$ 
is created. Then, for any global pattern $P$, there must exist at least one partition $Par_i$
such that $P$ is also a pattern in $Par_i$.
\end{theorem}
\begin{proof}
PROOF BY CONTRADICTION, OMITTED FOR NOW
\end{proof}

Utilizing Theorem~\ref{thm:replication_partition}, we create, for each snapshot $S_t$, 
a partition containing its next $(K-1)*G+K$ snapshots. Each partition is then
sending to the executors as a task. Since any global pattern must exists in 
one of the partitions, we can mine the patterns from each partitions independently.

\subsubsection{Temporal Replication Mining}
After replication, each task in Spark will process an interval of snapshots $Par_i$. The next
step is to mine the GCMPs from $Par_i$. We notice that, for each 
partition, we only need to find the patterns that
are contained in the first snapshots. Therefore we design a line-sweep method for mining 
such patterns. DETAILS OMITTED FOR NOW.

The Temporal Replication and Mining approach though achieves parallelism from independent
partitions, it requires to replicate the data multiple times. 
Specifically, each snapshots are copied $(K-1)*G+K$ times. In swarm
case, $G$ is as large as $|T|$. Then, it is equivalent to shuffle entire dataset 
to each executor, which is clearly inefficient.

\subsection{Star Partition and Mining}
To develop a method that achieves parallelism under any pattern parameters, 
we propose a solution called \emph{Star Partition and Mining}. In SPM,
we design a novel object-based partition method named star partition. In star partition,
instead of partitioning trajectories in temporal domain, we partition trajectories 
in object domain. After partitioning, we use the \emph{Apriori}-like 
method to mine the patterns out of each partition. 
The outline of the start partition and mining is as in Algorithm~\ref{algo:spm_overview}

@@

\subsubsection{Star Partition}
The purpose of star partition is to find the group of object that 
could potentially form a pattern. In order to achieve parallelism, 
we find and group, for each object $o$, all other objects that connect to $o$ in some
snapshots. By so doing, the patterns containing $o$ can be discovered within
each groups. Technically, we create a connection graph to represent the
connectivity among objects. A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= T$ 
represents the connection between vertex $s,t$ at all times in $T$, 
i.e. $\forall t \in T, C_t(s) = C_t(t)$. 
Given a vertex $s$, the star of $s$, $Sr_s$ is the set of incidental edges of $s$ in $G$.
In star partition, the trajectories are partitioned based on objects and their stars. Then
each partition is send to an executor as a task.
We state the completeness of star-partition as in the following theorem:
\begin{theorem}[Completeness of Star Partition]
Given a connection graph $G$, for any global pattern $P$, there exists a $s \in G.V$ such 
that $P$ is a pattern in $Sr_s$.
\end{theorem}

\begin{proof}
OMITTED FOR NOW
\end{proof}

Based on the above theorem, each task can be processed independently by executors. 
Thus, the inter-executor communication is avoided during the mining phase. It is notable that, the 
replication of data is $O(|\mathbb{O}|^2|T|)$, which is regardless the parameters of patterns.
In later sections, we will describe optimization techniques to reduce the replications.

\subsubsection{Apriori Mining}
For each task, in the mining phase, we need to find the patterns that conform to the parameter
setting. To systematically discover the patterns, we design the \emph{Apriori Mining} method which
is similar to frequent item mining. If a candidate pattern's object set is of size $R$, we call
this candidate a $R$-pattern. Our apriori mining algorithm tries to generate all $R$-pattern in
each iteration. As a start, the $2$-pattern is generated from edges in $Sr_s$. In particular,
for each $e(s,t)=T$, pattern $p=(\{s,t\}, T)$ is formed. During each iteration $R$, 
we generate $R+2$-cluster pattern by joining $(R+1)$-cluster patterns with $2$-cluster patterns. 
The join between $p_1=(O_1, T_1)$ and $p_2=(O_2, T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2, T_1 \cap T_2)$.
Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}
\Require{$Sr_s$}
\State { Lv $\gets \{\}$}
\State { Lv2 $\gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State Lv2.add($\langle \{s,t\}, T \rangle$);
\State Lv $\gets$ Lv2;
\EndFor
\While{true}
	\If{Lv is not empty} 
		\State{LvCand $\gets \{\}$ }
		\ForAll{$cand_v \in Lv$}
			\ForAll{$cand \in Lv2$}
				\State $p \gets cand_v$ join $cand$
				\If{$p.T$ is partly valid} 
					\State LvCand.add($p$)
				\EndIf
			\EndFor
		\EndFor
		\State {Lv $\gets$ LvCand}
	\Else
		\State{break}
	\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

Algorithm~\ref{algo:apriori_mining} takes exponential complexity to mine GCMP. There
are two major factors dragging the performance. First, the size of $Sr_s$ affects
the number initial size of $2$-patterns. Second, the level that apriori runs. In later
sections, we exploit the property of GCMP to reduce the two factors.

>>>>

\section{Preliminary on Apache Spark}
Apache Spark is an open sourced modern parallel processing platform
based on Resilient-Distributed-Dataset (RDD). Each RDD is able to take an action (including Map, Reduce, GroupByKey etc.) and then transforms to a new RDD. Algorithms in Spark is implemented by supplying various actions to an input RDD. Each RDD in Spark has a pre-defined and fixed number of partitions, where each partition forms a task assigned to an executor.

Compared to MapReduce, Spark 
utilizes distributed memory to cache the programming data modeled as RDDs, which brings computational benefits~\cite{shi2015clash}. In order to fully utilize the memory, Spark creates one thread for each task and then multiple tasks belonging to the same JVM share the available memory.
Due to threading, there is a paradigm shift from MapReduce to Spark. In MapReduce, the cost of starting a task is expensive, as each task in MapReduce requires a dedicated JVM process. While in Spark, the cost of starting a task is negligible since each task is done by a thread.  Therefore in Spark, we may create many more parallel tasks than in MapReduce before reaching to the system limitation.

\section{Mining Generalized Co-moving Pattern}
There are two stages in mining GCMP. The first stage is to cluster objects in each snapshots. Then the seconds stage is to mine patterns from clusters in parallel. The overview of the parallel approach is 
shown in Figure~\ref{fig:overview}. As shown, trajectory data is initially stored in HDFS. The first stage is to 
read trajectories and cluster objects in the same snapshots. Since the objects at each snapshots are independent, this stage can be easily performed in parallel. The first stage involves network IO. Afterwards, the clusters in each snapshots are shuffled and replicated to make various partitions.
In order to discover all patterns, we require a partitioning method to be \emph{complete} and \emph{Sound}.

\begin{definition}[Completeness and Soundness]
Let a partitioning method $\mathbb{P}$ partitions original trajectories $TR$ into multiple parts, $Par_1,...,Par_m$. $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $TR$, $\exists Par_i$ such that $P$ is valid in $Par_i$. $\mathbb{P}$ is sound if for all patterns $P$ that is valid in any $Par_i$, it is also valid in $TR$.
\end{definition}
The completeness ensures that no real patterns are missed out. The soundness ensures that no false patterns are reported. If a partition method is both sound and complete, we are then able to mining patterns in each resulted partition in parallel.

Depends on the pattern mining strategy, the size of shuffle and replication may differ. We show that if the pattern mining strategy is not selected carefully, the second stage will suffer from large data replication and shuffling.

\begin{figure} [h]
\center
\includegraphics[width=0.5\textwidth]{system_layout.jpg}
\caption{System Flow of Mining GCMP}
\label{fig:overview}
\end{figure}

\subsection{Temporal Replication and Mining}
The straightforward strategy of parallelizing the second stage is to vertically partition the trajectories based on snapshots. 
A simple but effective method
is to group neighborhood snapshots into a partition, such that every possible pattern can be mined within some of the partitions. In order to achieve the \emph{completeness},
some of the snapshots need to be replicated on multiple executors.
We call this method the \emph{Temporal Replication and Mining} approach. 
The algorithm is presented as in Algorithm~\ref{algo:trm_overview}.

@@

\subsubsection{Temporal Replication Partition}
In order to reduce the shuffling cost, the data to be replicated should be
kept to a minimum. However, as suggested in the following theorem, the minimum replication of a snapshot is not small:

\begin{theorem}[Soundness and Completeness of Replication]
\label{thm:replication_partition}
For each snapshot $S_t$, a partition $Par_t = \{S_t, ...,S_{t+(\lfloor \frac{K}{L}-1\rfloor *G+K)}\}$ 
is created. Such a partition method is sound and complete.
\end{theorem}
\begin{proof}
The soundness of partition is trivially true by definition.
Given a valid pattern $P$, let $T' \subseteq P.T$ be a subsequence of $P.T$ which conforms to $K,L,G$. Note that there could be many qualified $T'$ of $T$. Then, 
let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. Since $T'$ conforms to $K,L,G$, then $\Sigma_i (l_i) \geq K$, and $K \geq l_i \geq L$, $g_i \leq G$. Therefore, among all possible $T'$s, the minimum size is $\lfloor \frac{K}{L}-1\rfloor *G+K$. Thus ensuring each $Par_t$ to be of that size would capture one of the $T'$s, therefore the pattern $P$ is valid in $Par_t$. This proves the completeness of the partitioning method.
\end{proof}

Utilizing Theorem~\ref{thm:replication_partition}, we create, for each snapshot $S_t$, 
a partition containing its next $\lfloor \frac{K}{L}-1\rfloor *G+K$ snapshots. Each partition is then
sent to the executors as a task. Since any global pattern must exists in one of the partitions, we can mine the patterns from each partitions independently, without loss of patterns.

\subsubsection{Temporal Replication Mining}
After replication, each task in Spark will process an partition $Par_i$. The next
step is to mine the GCMPs from $Par_i$. We notice that, for each 
partition, we only need to find the patterns that
are contained in the first snapshots. Therefore we design a line-sweep method for mining 
such patterns, which is the variant of the Coherent-Moving-Clustering method in~\cite{jeung2008convoy}.

The Temporal Replication and Mining approach though achieves parallelism from independent
partitions, it requires to replicate the data multiple times. 
Specifically, each snapshots are copied $(K-1)*G+K$ times. In swarm
case, $G$ is as large as $|\mathbb{T}|$. In such a case, it is equivalent to replicate the entire dataset 
to each executor, which is clearly inefficient.

\subsection{Star Partition and Mining}
To develop a method that achieves parallelism under any pattern parameters, 
we propose the \emph{Star Partition and Mining} (SPM) method. In SPM,
we design a novel object-based partition method named star partition. A start partition partitions trajectories in the object domain rather than temporal domain. After partitioning, we design the \emph{Apriori}-like 
method to mine the patterns out of each partition independently. 
The overview of the star partition and mining is as in Algorithm~\ref{algo:spm_overview}.

@@

\subsubsection{Star Partition}
The purpose of star partition is to find the group of objects that 
could potentially form a pattern. In order to achieve parallelism, 
we group, for each object $o$, all other objects that connect to $o$ in some snapshots. By so doing, the patterns containing $o$ can be discovered within each groups. 
Technically, we create a connection graph to represent the
connectivity among objects. A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= ET$ 
contains all the timestamps where $s,t$ are in the same cluster,
i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
Given a vertex $s$, the star of $s$, $Sr_s$ is the set of incidental edges of $s$ in $G$. An example of star partition is shown in Figure~\ref{fig:star_partition}.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{star_partition.jpg}
\caption{Example of Star Partition}
\label{fig:star_partition}
\end{figure}

In star partition, trajectories are partitioned based on objects and their stars. Then
each partition is send to an executor as a task. 
Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. This is done by treating each vertex in $Sr_s$ as an object. For $s$, the time sequence is the union of all edges in $Sr_s$. For vertex $v \neq s$, the time sequence is the edge $(s,v)$.
Then, we state the completeness of star-partition as in the following theorem:
\begin{theorem}[Soundness and Completeness of Star Partition]
Star partition is sound and complete.
\end{theorem}

\begin{proof}
For the soundness,
if $P$ is a valid pattern in $Sr_s$, then for every object $v\neq s, v \in P.O$, and for every timestamp $t\in P.T$, $C_t(v) = C_t(s)$. This means, for every snapshot $t$, all object in $P.O$ belongs to the same cluster. Thus, $P$ is a valid pattern in original trajectories.

For the completeness,
if $P$ is a valid pattern in original trajectories, for an arbitrary object $s \in P.O$, it follows $P.O \equiv S_r$. Since for any time $t$, $C_s(t) = C_v(t) \forall v \in P.O$, every time in $P.T$ appears in edges in $Sr_s$, thus $P$ is valid pattern in $Sr_s$.
\end{proof}

Based on the above theorem, each star can be processed independently by executors, which avoids the inter-executor communication during the mining phase. It is notable that, the 
replication of data is $O(|\mathbb{O}|^2|\mathbb{T}|)$, which is free from the parameters of patterns.
In later sections, we will describe optimization techniques to reduce the replications.

\subsubsection{Apriori Mining}
For each task, in the mining phase, we need to find the patterns that conform to the parameters. To systematically discover the patterns, we design the \emph{Apriori Mining} method which
is similar to frequent item mining. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $|R|$. 
Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
we generate $(R+1)$-cluster patterns by joining $R$-cluster patterns with $2$-cluster patterns. Specifically,
the join between $p_1=(O_1, T_1)$ and $p_2=(O_2, T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2, T_1 \cap T_2)$. Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-cluster at most to a $(R+1)$-cluster.
Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}
\Require{$Sr_s$}
\State { Lv $\gets \{\}$}
\State { Ground $\gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State Ground.add($\langle \{s,t\}, T \rangle$);
\State Lv $\gets$ Ground;
\EndFor
\While{true}
	\If{Lv is not empty} 
		\State{LvCand $\gets \{\}$ }
		\ForAll{$cand_v \in Lv$}
			\ForAll{$cand \in $Ground}
				\State $p \gets cand_v$ join $cand$
				\If{$p.T$ is partly valid} 
					\State LvCand.add($p$)
				\EndIf
			\EndFor
		\EndFor
		\State {Lv $\gets$ LvCand}
	\Else
		\State{break}
	\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

Algorithm~\ref{algo:apriori_mining} takes exponential complexity to mine GCMP. There
are two major factors dragging the performance. First, the size of $Sr_s$ affects
the initial size of $2$-patterns. Second, the candidates generated in each level affects the join performance. In later
sections, we exploit the property of GCMP to reduce the two factors.
